---
title: "R Assignment 2"
author: "James Wang"
date: "10/18/2021"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Chapter 3 Exercise 37
Reading in the T-shirt data
```{r}
library(readxl)
tshirt_data <- read_excel("C:/Users/54208/Google Drive/School/Graduate School/Masters/Fall 2021/DataMining/jaggia_ba_1e_ch03_TShirts.xlsx")
```


```{r}
tshirt_size_color <- table(tshirt_data$Size,tshirt_data$Color)
tshirt_size_color
```
There were 43 Red M shirts sold and 33 Purple XL shirts sold

```{r}
tshirt_size_color.matrix <- as.matrix(tshirt_size_color)
heatmap(tshirt_size_color.matrix, col = heat.colors(256), scale = "none", Rowv= NA, Colv = NA)
```
Medium Purple and Small green are the most popular combinations. Small Blue and Small Yellow are the least popular combination

## Chapter 3 Exercise 63
Reading in gas data
```{r}
gas_data <- read_excel("C:/Users/54208/Google Drive/School/Graduate School/Masters/Fall 2021/DataMining/jaggia_ba_1e_ch03_GAS_2019.xlsx")
```

Constructing box plot for price
```{r}
boxplot(gas_data$Price)
```
Based off of the box plot, there is an outlier for gas price

Calculating Z-score
```{r}
mean(gas_data$Price)
sd(gas_data$Price)

gas_data$price_zscore <- (gas_data$Price - mean(gas_data$Price))/ sd(gas_data$Price)

which(gas_data$price_zscore > 3 | gas_data$price_zscore < -3)

```
No, my results are not consistent with part A. Based off of the Z-score values, none of the price are outliers. None of the prices' Z-score are higher than 3 or less than -3. There is a value that is at 2.7, so there is one that is close to being an outlier, but it's still within the acceptable range.

Removing outliers and replacing with NA values
```{r}
outlier_values <- boxplot(gas_data$Price,plot=FALSE)$out

outlier_values

gas_data[gas_data$Price %in% outlier_values, "Price"] = NA

gas_data$Price

mean(gas_data$Price,na.rm=TRUE)
```




